PUT YOUR TITLE HERE

### 2023-03-17 paper/manuscript.Rmd
stuff

d <- read_csv(here("data", "processed_data.csv"))
```

@@

# TODO list
- title
- abstract
- need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
- how to introduce coding methods (outcome measures)
- many citations everywhere
- long list of things to gesture at in intro
- link to open stuffs
- ** verify code for ES ** with someone

@@

[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem. Concerns about replication rates have become a large point of discussion in psychology and other fields.

@@

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from top psychology journals in 2008 [@openscienceconsortium2015]. They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature. [idk, maybe worth framing that this was a big deal study when it came out]. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

@@

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS @hoogeveen2019. RP:P looked at how replication rates varied across subsamples of their studies. They found that cognitive psychology studies replicated at higher, but still low rates (50% v 25%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates. There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.

[could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? @frank2012; @hawkins]
Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology. Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects. From this, we have 176 experimental replications that were codeable. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

## quick methods
[some of this should actually just go in methods methods] Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by ... Since around 2015, it has been required for incoming PhD students in the Psychology Department. Over the course of a quarter long class, students work through their individual replication projects, from choosing a study, to reimplementing it, to creating analysis code, piloting the study, pre-registering it, and finally running a full data collection and writing up their results. Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample). While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.

Studies vary along a number of dimensions, including statistical properties, subfield, and experimental properties. We leverage this naturally occurring variation to see if these properties predict replication success.

[again unclear the intro/ methods/results split]
Over the years, there have been a number of student projects, of these we are able to include 176 (see Figure \ref{fig:prisma} for exclusions). Because of variance in the experimental designs and reporting practices, we have variable statistical information. To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables. Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors. Other model results, including those from a sensitivity analysis, are available in the supplement.

As our primary outcome measure, we use a subjective measure of replication success. At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated. This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures. For robustness, first author independently coded all projects on the same scale off of the final write-ups. Disagreements (which occured foobar % of the time) were resolved by discussion between first and third authors.

As secondary outcomes, we also calculated prediction intervals following @errington2021 on the key measure of interest from each study. Because of variable statistics and reporting, this was calculable on FOOBAR studies.

Across the 176 studies, the overall replication rate was 49% TODO derive in code. FOOBAR % of the studies had replication outcomes within the prediction interval of the original outcome. The average p_original value (median?) was TODO.

For the FOOBAR studies with SMD, we see cite FIGURE.

## Single predictors
We drew a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some co-variates related to how close the replication would be. Many of these predictors individually correlate with subjective replication success (Figure \ref{tab:cor}. In particular, within-subjects designs, higher numbers of trials, and open data were predictive of replication. Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online were less likely to replicate. Distributions of study outcomes across some of these properties are shown in Figure TODO.

Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at a FOOBAR higher rate. Within and between subjects designs were both common, and within replicated at YY more. Similarly, studies with multiple vignettes replicated FOOBAR more. However, there are strong correlations between these experimental features and between experimental features and subfield.

TODO say somthing about openness

The study sample is split between studies that kept the same modality as the original (generally meaning that the original study used an online crowd-sourced sample) and those that switched. While TODO cite online studies are respectable, this does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

## Regression model
We were interested in determining what the strongest predictors were, which ones are most meaningful, so we threw it all into a big ol regularlized regression model. Despite this, wide uncertainty due to parameterization and stuff. The coefficients see Figure 3 ... TODO

@@

@@

@@

@@

@@

@@

@@

@@

### Measures of replication success
Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF. These were coded on a [0, .25, .5, .75, 1] scale.

>>>>

d <- read_csv(here("data", "processed_data.csv")) |> filter(status!="unusable")
```

@@

# TODO list
- title
- abstract
- need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
- how to introduce coding methods (outcome measures)
- many citations everywhere
- long list of things to gesture at in intro
- link to open stuffs
- ** verify code for ES ** with someone
- note that 4ish of these papers were previously reported in RP:P

# Citation slush pile

predict w/ ML @altmejd2019
prediction with humans @dreber2015; @forsell2019

econ also has replications and issues @camerer2016

moving goal posts around replication / interpreting results @nosek2020

some sort of modeling of replications @pawel2020

@@

[replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution] Concerns around the practices of science. Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem. Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.

@@

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from top psychology journals in 2008 [@openscienceconsortium2015]. They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature. The RP:P dataset was itself much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016] [idk, maybe worth framing that this was a big deal study when it came out]. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

@@

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS [@hoogeveen2019;@dreber2015; @forsell2019;@camerer2018]

RP:P looked at how replication rates varied across subsamples of their studies [@openscienceconsortium2015]. They found that cognitive psychology studies replicated at higher, but still low rates (50% v 25%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates.

There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences. TODO maybe foreshadow that there are reasons to believe there are correlations!

While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g. as a demonstration), or a low or uncertain prior (e.g. for a high-value study). When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.

Prior literature, such as @frank2012 and @hawkins have advocated using research methods classes to conduct replications, both for the education and scientific value.

Here we introduce a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

@@

PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF.  Over the course of 10 weeks, students choose a published finding to replicate, re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report. Students are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science. While this choice results in a non-random sampling of studies, the sample is representative of studies that are of interest to and doable by first year graduate students.

The sample of replicated studies reflects the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes. We leverage the naturally occuraing variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.

We used a subjective rating of replication success as our primary outcome measure. The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course. For reliability, we had a separate rater (VB) independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB. We focussed on this measure because it was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic [@errington2021].

@@

```{r}
sub_rep_rate <- d |> summarize(m=mean(sub_rep)*100)

pred_int_rate <- d |> filter(!is.na(predInt)) |> summarize(m=mean(as.numeric(predInt))*100)
porig_rate <- d |> filter(!is.na(p_orig)) |> summarize(m=median(p_orig)*100)
```
Across the 176 studies, the overall subjective replication rate was `r round(pluck(sub_rep_rate,1))`%. `r round(pluck(pred_int_rate,1))`% of the studies had replication outcomes within the prediction interval of the original outcome. The median p_original value was `r round(pluck(porig_rate, 1))`%. Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score. Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero. On average, there is a diminution of effect sizes from original to replication.

@@

## Single predictors
Properties of both the original study and the replication can influence whether or not the replication is a success. We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication would be. A full description of these features is given in methods.

Many of these predictors individually correlate with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, higher numbers of trials, and open data. Predictors of lower replicability included Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at twice the rate of social psychology studies. Within and between subjects designs were both common, and within replicated four times as much. Similarly, studies with multiple vignettes replicated 1.5 times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.

Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person).  While online studies in general show comparable results to studies conducted in person TODO CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

@@

## Regression model
While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another. In order to determine which predictors were the strongest, we ran a pre-registered regularized regression model (see Methods for details). The coefficient estimates are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients. The general directions of coefficients are consistent with the effects of the predictors in isolation. Within-subjects designs seem an especially strong indicator of replicability TODO include estimate and range in text!

Results from other models can be found in the supplement. TODO make this a true statement

@@

blah blah we did a thing and it generally aligns with prior results. Overall replication rate is consistent with prior work, and we find cog greater than soc. However, by looking at a greater range of pr

@@

circle back to the idea that student replications (either as class or before extension into their own work) would be valuable

@@

[some of this should actually just go in methods methods] Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by ... Since around 2015, it has been required for incoming PhD students in the Psychology Department.Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample). While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.

@@

### Measures of replication success
Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB’s coding disagreed with the staff/MCF’s code, the difference was resolved by discussion between VB and MCF. These were coded on a [0, .25, .5, .75, 1] scale. TODO rate of coding discrepancy

### 2023-03-17 paper/manuscript.tex
stuff

\begin{itemize}
\tightlist
\item
  title
\item
  abstract
\item
  need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
\item
  how to introduce coding methods (outcome measures)
\item
  many citations everywhere
\item
  long list of things to gesture at in intro
\item
  link to open stuffs
\item
  ** verify code for ES ** with someone
\end{itemize}

@@

{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem. Concerns about replication rates have become a large point of discussion in psychology and other fields.

@@

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from top psychology journals in 2008 (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature. {[}idk, maybe worth framing that this was a big deal study when it came out{]}. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

@@

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS Hoogeveen et al. (\protect\hyperlink{ref-hoogeveen2019}{2019}). RP:P looked at how replication rates varied across subsamples of their studies. They found that cognitive psychology studies replicated at higher, but still low rates (50\% v 25\%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates. There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.

(could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? \protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-hawkins}{Hawkins et al. n.d.})
Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology. Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects. From this, we have 176 experimental replications that were codeable. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

\hypertarget{quick-methods}{%
\subsection{quick methods}\label{quick-methods}}

{[}some of this should actually just go in methods methods{]} Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by \ldots{} Since around 2015, it has been required for incoming PhD students in the Psychology Department. Over the course of a quarter long class, students work through their individual replication projects, from choosing a study, to reimplementing it, to creating analysis code, piloting the study, pre-registering it, and finally running a full data collection and writing up their results. Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample). While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.

Studies vary along a number of dimensions, including statistical properties, subfield, and experimental properties. We leverage this naturally occurring variation to see if these properties predict replication success.

{[}again unclear the intro/ methods/results split{]}
Over the years, there have been a number of student projects, of these we are able to include 176 (see Figure \ref{fig:prisma} for exclusions). Because of variance in the experimental designs and reporting practices, we have variable statistical information. To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables. Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors. Other model results, including those from a sensitivity analysis, are available in the supplement.

As our primary outcome measure, we use a subjective measure of replication success. At the end of the class, the instruction team coded each project on a 0-1 scale indicating whether or not it replicated. This allows for nuance around marginal effects, covers studies with a broad range of statistical outcomes (including those that do not lend themselves to NHST), and includes studies with multiple important outcome measures. For robustness, first author independently coded all projects on the same scale off of the final write-ups. Disagreements (which occured foobar \% of the time) were resolved by discussion between first and third authors.

As secondary outcomes, we also calculated prediction intervals following Errington et al. (\protect\hyperlink{ref-errington2021}{2021}) on the key measure of interest from each study. Because of variable statistics and reporting, this was calculable on FOOBAR studies.

Across the 176 studies, the overall replication rate was 49\% TODO derive in code. FOOBAR \% of the studies had replication outcomes within the prediction interval of the original outcome. The average p\_original value (median?) was TODO.

For the FOOBAR studies with SMD, we see cite FIGURE.

We drew a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some co-variates related to how close the replication would be. Many of these predictors individually correlate with subjective replication success (Figure \ref{tab:cor}. In particular, within-subjects designs, higher numbers of trials, and open data were predictive of replication. Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online were less likely to replicate. Distributions of study outcomes across some of these properties are shown in Figure TODO.

Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at a FOOBAR higher rate. Within and between subjects designs were both common, and within replicated at YY more. Similarly, studies with multiple vignettes replicated FOOBAR more. However, there are strong correlations between these experimental features and between experimental features and subfield.

TODO say somthing about openness

The study sample is split between studies that kept the same modality as the original (generally meaning that the original study used an online crowd-sourced sample) and those that switched. While TODO cite online studies are respectable, this does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

We were interested in determining what the strongest predictors were, which ones are most meaningful, so we threw it all into a big ol regularlized regression model. Despite this, wide uncertainty due to parameterization and stuff. The coefficients see Figure 3 \ldots{} TODO

@@

@@

@@

@@

@@

@@

Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF. These were coded on a {[}0, .25, .5, .75, 1{]} scale.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
Camerer CF, Dreber A, Holzmeister F, Ho T-H, Huber J, Johannesson M, Kirchler M, Nave G, Nosek BA, Pfeiffer T, Altmejd A, Buttrick N, Chan T, Chen Y, Forsell E, Gampa A, Heikensten E, Hummer L, Imai T, Isaksson S, Manfredi D, Rose J, Wagenmakers E-J, Wu H (2018) Evaluating the replicability of social science experiments in {Nature} and {Science} between 2010 and 2015. \emph{Nat Hum Behav} \textbf{2}:637--644. doi:\href{https://doi.org/10.1038/s41562-018-0399-z}{10.1038/s41562-018-0399-z}

@@

@@

@@

@@

>>>>

\begin{itemize}
\tightlist
\item
  title
\item
  abstract
\item
  need to do supplement with the stuff we preregistered (sensitivity analysis, all models)
\item
  how to introduce coding methods (outcome measures)
\item
  many citations everywhere
\item
  long list of things to gesture at in intro
\item
  link to open stuffs
\item
  ** verify code for ES ** with someone
\item
  note that 4ish of these papers were previously reported in RP:P
\end{itemize}

\hypertarget{citation-slush-pile}{%
\section{Citation slush pile}\label{citation-slush-pile}}

predict w/ ML Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019})
prediction with humans Dreber et al. (\protect\hyperlink{ref-dreber2015}{2015}); Forsell et al. (\protect\hyperlink{ref-forsell2019}{2019})

econ also has replications and issues Camerer et al. (\protect\hyperlink{ref-camerer2016}{2016})

moving goal posts around replication / interpreting results Nosek \& Errington (\protect\hyperlink{ref-nosek2020}{2020})

some sort of modeling of replications Pawel \& Held (\protect\hyperlink{ref-pawel2020}{2020})

@@

{[}replication: it's a hot issue and concerns around replication have done a lot, see crisis/revolution{]} Concerns around the practices of science. Replication is a hot topic. Some argue that it is a cornerstone of a cumulative science, and findings of low replication rates are a problem. Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.

@@

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from top psychology journals in 2008 (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature. The RP:P dataset was itself much discussed and reanalyzed (\protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) {[}idk, maybe worth framing that this was a big deal study when it came out{]}. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

@@

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS (\protect\hyperlink{ref-dreber2015}{Dreber et al. 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al. 2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al. 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al. 2019})

RP:P looked at how replication rates varied across subsamples of their studies (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). They found that cognitive psychology studies replicated at higher, but still low rates (50\% v 25\%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates.

There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences. TODO maybe foreshadow that there are reasons to believe there are correlations!

While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.~as a demonstration), or a low or uncertain prior (e.g.~for a high-value study). When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.

Prior literature, such as Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012}) and Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.}) have advocated using research methods classes to conduct replications, both for the education and scientific value.

Here we introduce a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

@@

PSYCH 251 is Stanford Psychology's graduate-level experimental methods class taught by MCF. Over the course of 10 weeks, students choose a published finding to replicate, re-implement the study, write analysis code, pre-register their study, collect data using an online platform, and write up a structured replication report. Students are free to choose studies related to their research interests, with the default recommendation being an article from a recent year of Psychological Science. While this choice results in a non-random sampling of studies, the sample is representative of studies that are of interest to and doable by first year graduate students.

The sample of replicated studies reflects the variability of the literature, including studies from different subfields, using different experimental methods and statistical outcomes. We leverage the naturally occuraing variability in this sample of replications to examine how different demographic, experimental design, and statistical properties predict replication success.

We used a subjective rating of replication success as our primary outcome measure. The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course. For reliability, we had a separate rater (VB) independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB. We focussed on this measure because it was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (NUMBER, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al. 2021}).

@@

Across the 176 studies, the overall subjective replication rate was 49\%. 46\% of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 3\%. Figure \ref{fig:smd} shows the relationship between original SMD, replication SMD, and subjective replication score. Roughly speaking, there's a cluster of studies that replicate with similar effect sizes to the original and another cluster that fail to replicate with replication effect sizes near zero. On average, there is a diminution of effect sizes from original to replication.

@@

Properties of both the original study and the replication can influence whether or not the replication is a success. We chose a set of predictor variables from the correlational results of RP:P and our own intuitions about experimental factors that might impact replication success as well as some covariates related to how close the replication would be. A full description of these features is given in methods.

Many of these predictors individually correlate with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, higher numbers of trials, and open data. Predictors of lower replicability included Single vignetted studies, social psychology studies, and original-replication pairs where the replication switched to online.

Distributions of study outcomes across some of these properties are shown in Figure \ref{fig:predictors-graph}. Both social and cognitive psychology studies were well represented, and the cognitive psychology studies replicated at twice the rate of social psychology studies. Within and between subjects designs were both common, and within replicated four times as much. Similarly, studies with multiple vignettes replicated 1.5 times more than single vignetted studies. However, there were strong correlations among these experimental features and between these experimental features and subfield.

Studies with open data, which almost always also had open materials, tended to replicate more than studies without open data, although this may be linked to temporal trends.

Nearly all replications studies were conducted online, but original studies were split between using in-person and online recruitment. Replications that switched to online were less likely to replicate than those that had the same modality as the original (generally both online, in a few cases both in-person). While online studies in general show comparable results to studies conducted in person TODO CITATIONS, switching the modality does decrease the closeness of the replication, and some studies done in person may not have been well adapted (ex. inductions may be weaker or attention checks inadequate to the new sample).

@@

While a number of the predictors show individual correlations with the subjective replication score, many of the predictors are also correlated with one another. In order to determine which predictors were the strongest, we ran a pre-registered regularized regression model (see Methods for details). The coefficient estimates are shown in Figure \ref{fig:mod-results}. Due to a large number of predictors coupled with a small and noisy dataset, even with strong regularization, there is much uncertainty around the coefficients. The general directions of coefficients are consistent with the effects of the predictors in isolation. Within-subjects designs seem an especially strong indicator of replicability TODO include estimate and range in text!

Results from other models can be found in the supplement. TODO make this a true statement

@@

{[}some of this should actually just go in methods methods{]} Class, taught by last author, is an experimental methods class aimed at first-year graduate students, but taken by \ldots{} Since around 2015, it has been required for incoming PhD students in the Psychology Department.Students are free to choose studies related to their interests, although recent articles from Psychological Science are the recommended path under uncertainty (leading to a high proportion of Psych science articles in this replication sample). While the sampling procedure is non-random, it is generally representative of studies that are of interest to and doable by first year grad students.

@@

Our primary replication outcome is experimenter and instructor rated replication success (0-1). The subjective replication success was recorded by the teaching staff for the majority of class replications at the time they were conducted. Where the values were missing they were filled in by MCF on the basis of the reports. For all studies, replication success was independently coded by VB on the basis of the reports. Where VB's coding disagreed with the staff/MCF's code, the difference was resolved by discussion between VB and MCF. These were coded on a {[}0, .25, .5, .75, 1{]} scale. TODO rate of coding discrepancy

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-altmejd2019}{}}%
Altmejd A, Dreber A, Forsell E, Huber J, Imai T, Johannesson M, Kirchler M, Nave G, Camerer C (2019) Predicting the replicability of social science lab experiments. \emph{PLOS ONE} \textbf{14}:e0225826. doi:\href{https://doi.org/10.1371/journal.pone.0225826}{10.1371/journal.pone.0225826}

\leavevmode\vadjust pre{\hypertarget{ref-camerer2016}{}}%
Camerer CF, Dreber A, Forsell E, Ho T-H, Huber J, Johannesson M, Kirchler M, Almenberg J, Altmejd A, Chan T, Heikensten E, Holzmeister F, Imai T, Isaksson S, Nave G, Pfeiffer T, Razen M, Wu H (2016) Evaluating replicability of laboratory experiments in economics. \emph{Science} \textbf{351}:1433--1436. doi:\href{https://doi.org/10.1126/science.aaf0918}{10.1126/science.aaf0918}

\leavevmode\vadjust pre{\hypertarget{ref-camerer2018}{}}%
Camerer CF, Dreber A, Holzmeister F, Ho T-H, Huber J, Johannesson M, Kirchler M, Nave G, Nosek BA, Pfeiffer T, Altmejd A, Buttrick N, Chan T, Chen Y, Forsell E, Gampa A, Heikensten E, Hummer L, Imai T, Isaksson S, Manfredi D, Rose J, Wagenmakers E-J, Wu H (2018) Evaluating the replicability of social science experiments in {Nature} and {Science} between 2010 and 2015. \emph{Nat Hum Behav} \textbf{2}:637--644. doi:\href{https://doi.org/10.1038/s41562-018-0399-z}{10.1038/s41562-018-0399-z}

@@

\leavevmode\vadjust pre{\hypertarget{ref-dreber2015}{}}%
Dreber A, Pfeiffer T, Almenberg J, Isaksson S, Wilson B, Chen Y, Nosek BA, Johannesson M (2015) Using prediction markets to estimate the reproducibility of scientific research. \emph{Proc Natl Acad Sci} \textbf{112}:15343--15347. doi:\href{https://doi.org/10.1073/pnas.1516179112}{10.1073/pnas.1516179112}

@@

\leavevmode\vadjust pre{\hypertarget{ref-etz2016}{}}%
Etz A, Vandekerckhove J (2016) A {Bayesian Perspective} on the {Reproducibility Project}: {Psychology}. \emph{PLOS ONE} \textbf{11}:e0149794. doi:\href{https://doi.org/10.1371/journal.pone.0149794}{10.1371/journal.pone.0149794}

\leavevmode\vadjust pre{\hypertarget{ref-forsell2019}{}}%
Forsell E, Viganola D, Pfeiffer T, Almenberg J, Wilson B, Chen Y, Nosek BA, Johannesson M, Dreber A (2019) Predicting replication outcomes in the {Many Labs} 2 study. \emph{Journal of Economic Psychology} \textbf{75}:102117. doi:\href{https://doi.org/10.1016/j.joep.2018.10.009}{10.1016/j.joep.2018.10.009}

@@

\leavevmode\vadjust pre{\hypertarget{ref-gilbert2016}{}}%
Gilbert DT, King G, Pettigrew S, Wilson TD (2016) Comment on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037. doi:\href{https://doi.org/10.1126/science.aad7243}{10.1126/science.aad7243}

@@

\leavevmode\vadjust pre{\hypertarget{ref-nosek2020}{}}%
Nosek BA, Errington TM (2020) The best time to argue about what a replication means? {Before} you do it. \emph{Nature} \textbf{583}:518--520. doi:\href{https://doi.org/10.1038/d41586-020-02142-6}{10.1038/d41586-020-02142-6}

\leavevmode\vadjust pre{\hypertarget{ref-patil2016}{}}%
Patil P, Peng RD, Leek JT (2016) What {Should Researchers Expect When They Replicate Studies}? {A Statistical View} of {Replicability} in {Psychological Science}. \emph{Perspect Psychol Sci} \textbf{11}:539--544. doi:\href{https://doi.org/10.1177/1745691616646366}{10.1177/1745691616646366}

\leavevmode\vadjust pre{\hypertarget{ref-pawel2020}{}}%
Pawel S, Held L (2020) Probabilistic forecasting of replication studies. \emph{PLOS ONE} \textbf{15}:e0231416. doi:\href{https://doi.org/10.1371/journal.pone.0231416}{10.1371/journal.pone.0231416}
